---
title: "PML-Assignment"
author: "Shyam Naren"
date: "Sunday, April 26, 2015"
output: html_document
---

Load All Packages

```{r}

library(caret)
library(Hmisc)
library(data.table)
library(kernlab)

```

Load Sample Data & Test Data (data to be predicted)
```{r}

setInternet2(TRUE)
sample_data_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
sample_data <- fread(sample_data_url)

test_data_url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
test_data <- fread(test_data_url)
```
Use all Belt, arm, dumbbell, and forearm variables that don't have NAs in the test data as predictors
```{r}

VarStatus <- sapply(test_data, function (x) any(is.na(x) | x == ""))
PredictorStatus <- !VarStatus & grepl("belt|[^(fore)]arm|dumbbell|forearm", names(VarStatus))
PredictorList <- names(VarStatus)[PredictorStatus]

```
#Add classe variable as well & subset sample & test data to include selected predictors

```{r}
PredictorList<-c(PredictorList,"classe")
sample_data <- sample_data[, PredictorList, with=FALSE]
test_data <- test_data[, PredictorList, with=FALSE]

sample_data$classe<-as.factor(sample_data$classe)
test_data$classe<-as.factor(test_data$classe)
```
Set up & Train SVM 
```{r}
sigDist <- sigest(classe ~ ., data = Train_data, frac = 1)
### creating a grid of two tuning parameters, .sigma comes from the earlier line. we are trying to find best value of .C
svmTuneGrid <- data.frame(.sigma = sigDist[1], .C = 2^(-4:10))

model <- train(classe ~ .,
           data = Train_data,
           method = "svmRadial",
           preProc = c("center", "scale"),
           tuneGrid = svmTuneGrid,
           trControl = trainControl(method = "repeatedcv", repeats = 5, 
                                    classProbs =  TRUE))
```

Test Model on probe data to get a sense of Out of Sample Error
```{r}
pred <- predict(model,Probe_data[,1:52])
cmatrix <- confusionMatrix(pred,Probe_data$classe)
```
Confusion Matrix shows 100% accuracy, so try the model on test data
```{r}
pred <- predict(model,test_data[,1:52])
```
